A Combinatorial Search of Parameterized Quantum Circuit Learning for Chemical Applications

### 2025-02-13 manuscript/main.tex
Mon  3 Feb 2025 17:14:19 EST manuscript
Thu Feb 13 06:15:42 PM EST 2025 manuscript + error mitigation

@@

\subsection{Implementation}
We perform all simulation calculations using PennyLane\cite{bergholm_pennylane_2022}, either using Qulacs\cite{suzuki_qulacs_2021} for state vector calcualtions, while noisy calculations were performed using \textit{qiskit-aer} with the \textit{FakeQuebec} backend as implemented in the PennyLane-Qiskit plugin.\cite{javadi-abhari_quantum_2024}
We perform calculations in the \textit{ibm\_quebec} device using circuits implemented using Qiskit\cite{javadi-abhari_quantum_2024}, due to issues we initially faced with running experiments on the real device using the PennyLane-Qiskit plugin.
For the experiments using PennyLane,  we utilize the Simultaneous Perturbation Stochastic Approximation method (SPSA) as implemented in PennyLane, while for the experiments run on \textit{ibm\_quebec} utilizes the Constrained Optimization By Linear Approximation (COBYLA) optimizer as implemented ing SciPy\cite{virtanen_scipy_2020}.
Each optimizer was chosen based on the performance for the given task.
All features ($\mathbf{x}$) and target values ($\mathbf{y}$) were scaled using the MinMaxScaler in Scikit-learn\cite{pedregosa_scikit-learn_2011}, such that all featues and target values are $\mathbb{R}\in [ -1,1 ]$.
For the simulations using \textit{FakeQuebec} and experiments on \textit{ibm\_quebec} we utilize Twirled Readout Error eXtinction (TREX) error mitigation.

@@

@@

\subsection{BSE}
The first chemically relevant dataset we explore in this study is the BSE49 dataset.
As highlighted in Figs. \ref{fig:bondtypes} and \ref{fig:BSEdistr}, this dataset consists of a diverse set of representative chemical bonds and bond separation energies.
Herein, we follow a similar analysis to the function fitting data, starting off with an analysis of a large set of PQCs using five and sixteen qubits with RUDs and ALs of 1.
From these two sets of data, we choose the best two models to study how an increase in the RUD and AL effects model performance.
[learning curves]
[Conclude we do not want to run this on real hardware due to the lack of promising results using simulation]

@@

\ref{fig:bse5rudal}

\ref{fig:bse16rudal}

\begin{figure}[H]
	\centering	
	\begin{subfigure}[b]{0.49\textwidth}
		\centering
		\includegraphics[width=\linewidth]{../images/BSE/fivequbit/BSE5_RUDAL}
		\caption{}
		\label{fig:bse5rudal}
	\end{subfigure}
	\hfill
	\begin{subfigure}[b]{0.49\textwidth}
		\centering
		\includegraphics[width=\linewidth]{../images/BSE/sixteenqubit/BSE16_RUDAL}
		\caption{}
		\label{fig:bse16rudal}
	\end{subfigure}
	\caption{}
	\label{fig:BSE_RUD_AL}	
\end{figure}

\begin{figure}[H]
	\centering
	\includegraphics[width=0.7\linewidth]{../images/BSE/fivequbit/BSE5_learning_curves}
	\caption{}
	\label{fig:bse5learningcurves}
\end{figure}

@@

\begin{figure}[H]
	\centering
	\includegraphics[width=\linewidth]{../images/DDCC/DDCC_RUDAL}
	\caption{Model evaluation, using R$^{2}$ (y-axis), of re-upload depths (RUD) and ansatz layers (AL) of 1, 3, and 5 for the A2\_HWE-CNOT using the DDCC dataset. The left side of the plot denotes the training set and the right side the test set.}
	\label{fig:ddccrudal}
\end{figure}

>>>>

We introduce \textit{qregress}, a modular Python-based code built on PennyLane for exploring PQCs for regression based learning tasks.
We analyze three datasets, a function fitting dataset, used for model calibration, and two chemically relevant datasets that offer challenging learning tasks for PQCs.

@@

\subsection{Implementation}
\begin{figure}[H]
	\centering
	\includegraphics[width=\linewidth]{../images/manuscript_figures/overview.png}
	\caption{Make this figure highlight the modularity of \textit{qregress}}
	\label{fig:overview_project}
\end{figure}

We introduce \textit{qregress}, a modular Python package for regression-based PQCs.

We perform all simulation calculations using PennyLane\cite{bergholm_pennylane_2022}, either using Qulacs\cite{suzuki_qulacs_2021} for state vector calcualtions, while noisy calculations were performed using \textit{qiskit-aer} with the \textit{FakeQuebec} backend as implemented in the PennyLane-Qiskit plugin.\cite{javadi-abhari_quantum_2024}
We perform calculations in the \textit{ibm\_quebec} device using circuits implemented using Qiskit\cite{javadi-abhari_quantum_2024}, due to issues we initially faced with running experiments on the real device using the PennyLane-Qiskit plugin.
For the experiments using PennyLane,  we utilize the Simultaneous Perturbation Stochastic Approximation method (SPSA) as implemented in PennyLane, while for the experiments run on \textit{ibm\_quebec} utilizes the Constrained Optimization By Linear Approximation (COBYLA) optimizer as implemented ing SciPy\cite{virtanen_scipy_2020}.
Each optimizer was chosen based on the performance for the given task.
All features ($\mathbf{x}$) and target values ($\mathbf{y}$) were scaled using the MinMaxScaler in Scikit-learn\cite{pedregosa_scikit-learn_2011}, such that all featues and target values are $\mathbb{R}\in [ -1,1 ]$.
For the simulations using \textit{FakeQuebec} and experiments on \textit{ibm\_quebec} we utilize Twirled Readout Error eXtinction (TREX) error mitigation.

@@

optimization level needs to be set to 0!

@@

\subsection{BSE}
The first chemically relevant dataset we explore is the BSE49 dataset.
As highlighted in Figs. \ref{fig:bondtypes} and \ref{fig:BSEdistr}, this dataset consists of a diverse set of representative chemical bonds and bond separation energies.
Herein, we follow a similar analysis to the function fitting data, starting off with an analysis of a large set of PQCs using five and sixteen qubits with RUDs and ALs of 1.
From these two sets of data, we choose the best two models to study how an increase in the RUD and AL effects model performance.
[learning curves]
[Conclude we do not want to run this on real hardware due to the lack of promising results using simulation]

@@

\begin{figure}[H]
	\centering	
	\begin{subfigure}[b]{0.49\textwidth}
		\centering
		\includegraphics[width=\linewidth]{../images/BSE/fivequbit/BSE5_RUDAL_lineplot}
		\caption{}
		\label{fig:bse5RUDAL_lineplot}
	\end{subfigure}
	\hfill
	\begin{subfigure}[b]{0.49\textwidth}
		\centering
		\includegraphics[width=\linewidth]{../images/BSE/sixteenqubit/BSE16_RUDAL_lineplot}
		\caption{}
		\label{fig:bse16RUDAL_lineplot}
	\end{subfigure}
	\hfill
	\begin{subfigure}[b]{\textwidth}
		\centering
		\includegraphics[width=\linewidth]{../images/BSE/fivequbit/distribution_parity}
		\caption{}
		\label{fig:BSE5_distribution_parity}
	\end{subfigure}
	\hfill
	\begin{subfigure}[b]{\textwidth}
		\centering
		\includegraphics[width=\linewidth]{../images/BSE/sixteenqubit/distribution_parity}
		\caption{}
		\label{fig:BSE16_distribution_parity}
	\end{subfigure}
	\caption{}
	\label{fig:BSE_distribution_parity}	
\end{figure}

\begin{figure}[H]
	\centering	
	\begin{subfigure}[b]{0.49\textwidth}
		\centering
		\includegraphics[width=\linewidth]{../images/BSE/fivequbit/BSE_learningcurve}
		\caption{}
		\label{fig:BSE5_learning_curves}
	\end{subfigure}
	\hfill
	\begin{subfigure}[b]{0.49\textwidth}
		\centering
		\includegraphics[width=\linewidth]{../images/BSE/sixteenqubit/BSE_learningcurve}
		\caption{}
		\label{fig:BSE16_learningcurve}
	\end{subfigure}
	\caption{}
	\label{fig:BSE_LC}	
\end{figure}

@@

\begin{figure}[H]
	\centering	
	\begin{subfigure}[b]{0.49\textwidth}
		\centering
		\includegraphics[width=\linewidth]{../images/DDCC/DDCC_RUDAL_lineplot}
		\caption{}
		\label{fig:ddccRUDAL_lineplot}
	\end{subfigure}
	\hfill
	\begin{subfigure}[b]{\textwidth}
		\centering
		\includegraphics[width=\linewidth]{../images/DDCC/distribution_parity}
		\caption{}
		\label{fig:ddccdistribution_parity}
	\end{subfigure}
	\caption{Model evaluation, using R$^{2}$ (y-axis), of re-upload depths (RUD) and ansatz layers (AL) of 1, 3, and 5 for the A2\_HWE-CNOT using the DDCC dataset. The left side of the plot denotes the training set and the right side the test set.}
	\label{fig:ddcc_rud}	
\end{figure}

\begin{figure}[H]
	\centering
	\includegraphics[width=\linewidth]{../images/DDCC/DDCC_learning_curves}
	\caption{}
	\label{fig:ddcclearningcurves}
\end{figure}
